\chapter*{Acknowledgments}

There are no proper words to convey my deep gratitude and respect for my thesis and research advisor, Dr. Sudeepto Bhattacharya, Shiv Nadar University, India. With his course in graph theory and complex network, he not only inculcated my interest in graph theory, but has inspired me to become an independent researcher. He helped me realize the power of critical reasoning, simple, but concrete mathematical representation of idea and guidance to recover when my steps faltered.

I would like to express my gratitude to my  external supervisor at Skolkovo Institute of Science and Technology, Moscow, Russia Federation,  Dr. Anatoly Dymarsky and Dr. Panagiotis Karras,  whose expertise, understanding, and patience, added considerably to my thesis experience. They taught me how to critically question thoughts and express ideas in simple but scientific way. Their insightful thought-provoking comments and constructive criticisms at different stages of my research allowed me to stay focused to core of research ideas. I am grateful to them for holding me to a high research standard and enforcing strict validations for each research result, and thus teaching me how to do research.

My sincere thanks must also go Dr. George Ovchinnikov, without whose motivation and encouragement I would not have considered working on Bitcoin and graph kernels. It was under his tutelage that I developed a focus and became interested in science behind Bitcoin. He provided me with direction, technical support and became more of a mentor and friend, than a guide. It was though his, persistence, understanding and kindness that I completed my master thesis in utter joy. I doubt that I will ever be able to convey my appreciation fully, but I owe him my eternal gratitude.

There is no way to express how much it meant to me to have been a member of Center for Computational and Data-Intensive Science and Engineering Lab for all meaningful discussion on different plethora  of research topics. The brilliant friends, colleagues and and all the other current and former Lab graduates students and visitors that I know inspired me over my stay in Moscow. Also, thanks to active communities of Bitcoin, R, Gephi and Python.

I would like to thank all the people associated with Big Data Analytics Center, Shiv Nadar University, fellow students and teachers who have been source of thoughts, inspiration and smiles. Acknowledgement will be incomplete without expressing sincere gratitude to Dr. Santosh Singh for providing excellent infrastructure, guidance and scholastic path to realize our dreams into reality.

Though only some name appears on the cover of this thesis, a great many people have contributed to its production. I owe my deep gratitude to all those people who have made this thesis possible and because of whom my graduate experience has been one that I will cherish forever. 

I deeply thank my family for their unconditional trust, timely encouragement, and endless patience. It was their love that raised me up again when I got weary.

In conclusion, I recognize that this research would not have been possible without the financial assistance of Skolkovo Institute of Science and Technology, Moscow, Russian Federation and Shiv Nadar University, India (Teaching Assistantships, Visiting Research Scholarships) , and express my gratitude to those agencies.
   
\begin{flushright}
Pankaj Kumar
\end{flushright}



