\begin{thebibliography}{99}
\setlength{\parskip}{1em}

\bibitem{Lo2015} Lo, S and Wand, C. 
\newblock Bitcoin as Money?.
\newblock {\em Federal Reserve Bank of Boston, Current Policy Perspective}. 14-4, Boston.
\newblock \url {http://www.bostonfed.org/economic/current-policy-perspectives/2014/cpp1404.pdf}, 2015.

\bibitem{Kristoufek2015} Kristoufek,L.
\newblock What are the main drivers of the bitcoin price? evidence
from wavelet coherence analysis. 
\newblock {\em PLoS ONE}, 10(4), 04, 2015.

\bibitem{Donier2015} Donier, J and Bouchaud, J.
\newblock Why Do Markets Crash? Bitcoin Data Offers Unprecedented Insights.
\newblock {\em PLoS ONE}, 10(10): e0139356, 2015.

\bibitem{Ali2014}
Ali, R, Barrdear, J, Clews, J and Southgate, J.
\newblock The economics of digital currencies.
\newblock {\em Bank of England Quarterly Bulletin}, page~Q3, 2014.

\bibitem{Nakamoto2008} Nakamoto, S.
\newblock Bitcoin: A peer-to-peer electronic cash system.
\newblock {\em Consulted}, 1(2012):28, 2008.

\bibitem{Kondor2014} Kondor, D, Csabai, I, Sz{\"{u}}le, J, P{\'{o}}sfai, M and Vattay,  G.
\newblock Inferring the interplay between network structure and market
effects in bitcoin.
\newblock {\em New Journal of Physics}, 16(12):125003, 2014.

\bibitem {Zager2008} Zager, L and Verghes, G. 
\newblock Graph similarity scoring and matching. 
\newblock {\em Applied Mathematics Letters}, 21(1):86 – 94, 2008.

\bibitem{Yanardag2015} Yanardag, P and Vishwanathan, S.V.N. 
\newblock Deep graph kernels. 
\newblock {\em In Proceedings of the 21th ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, KDD ’15, pages 1365–1374, New York, USA, 2015.

\bibitem {Johannes2015} Johannes G, Keeler P, Krzesinski, A and Taylor, P. 
\newblock Bitcoin blockchain dynamics: the selfish-mine strategy in the
presence of propagation delay.
\newblock {\em CoRR, abs/1505.05343},
\newblock \url {http://arxiv.org/abs/1505.05343}, 2015.

\bibitem {Blockchain2016}
\newblock \url {https://bitcoin.org/en/developer-guide#block-chain}

\bibitem {Ron2013} Ron, D and Shamir, A.
\newblock Quantitative Analysis of the Full Bitcoin Transaction Graph.
\newblock {\em IACR Cryptology ePrint Archive}, p. 584, 2013.

\bibitem {Reid2013} Reid, F and Harrigan, M.
\newblock An Analysis of Anonymity in the Bitcoin System.
\newblock {\em Security and Privacy in Social Networks}, pp 197-223, 2013.

\bibitem {Csabai2014} Kondor, D, Csabai, I, P{\'{o}}sfai, M and Vattay,  G.
\newblock Do the Rich Get Richer? An Empirical Analysis of the Bitcoin Transaction Network. 
\newblock {\em PLOS ONE}, 9(5): e97205., 2014.

\bibitem {Spagnuolo2013} Spagnuolo, M. 
\newblock Bitiodine: Extracting intelligence from the bitcoin network. 
\newblock {\em Master’s thesis, Politecnico di Milano, Italy}, 2013

\bibitem {Fleder2015} Fleder, M, Kester, M and Pillai, S.
\newblock Bitcoin transaction graph analysis. 
\newblock {\em CoRR}, abs/1502.01657,
\newblock \url {http://arxiv.org/abs/1502.01657}, 2015.

\bibitem {Babai2016} Babai, L. 
\newblock  Graph isomorphism in quasipolynomial time. 
\newblock {\em CoRR}, abs/1512.03547, 
\newblock \url {http://arxiv.org/abs/1512.03547}, 2016.

\bibitem {Lee2012} Lee, J, Han, W.S, Kasperovics, R and Lee, J.H.
\newblock  An in-depth comparison of subgraph isomorphism algorithms in graph databases. 
\newblock {\em VLDB}, pages 133–144, 2012.

\bibitem {Gao2010} Gao,X, Xiao, B, Tao, D and Li, X.
\newblock A survey of graph edit distance.
\newblock {\em Pattern Analysis and Applications}, Volume 13, Issue 1, pp 113-129, 2010.

\bibitem {Lerouge2016} Lerouge, L, Abu{-}Aisheh, Z, Raveaux, R, H{\'{e}}roux, P and Adam, S.
\newblock Graph edit distance : a new binary linear programming formulation.
\newblock {\em CoRR}, abs/1505.05740, 
\newblock \url {http://arxiv.org/abs/1505.05740}, 2016.

\bibitem {Koutra2015} Koutra,D, Vogelstein, J.T, and Faloutsos, C.
\newblock  DELTACON: A principled massive-graph similarity function. 
\newblock {\em CoRR}, abs/1304.4657,
\newblock \url {http://arxiv.org/abs/1304.4657}, 2015.


\bibitem {Li2012} Li, G, Semerci, M, Yener, M and Zaki, M.J. 
\newblock Effective graph classification based on topological and label attributes.
\newblock {\em Stat. Anal. Data Min.}, 5(4):265–283, August 2012.

\bibitem {Mheich2015} Mheich, A, Hassan, M, Gripon,V,  Khalil, M,  Berrou, C, Dufor, O and Wendling, F.
\newblock  A novel algorithm for measuring graph similarity:
Application to brain networks. 
\newblock {\em In Neural Engineering (NER), 2015 7th
International IEEE/EMBS Conference on}, pages 1068–1071, April 2015.

\bibitem {Melnik2002} Melnik, S,  Molina, H.G, and Rahm, E.
\newblock Similarity flooding: A versatile graph matching algorithm and its application to schema matching. 
\newblock {\em In Proceedings of the 18th International Conference on Data
Engineering, ICDE ’02,}, IEEE Computer Society, pages 117–, Washington, DC, USA, 2002. 

\bibitem {Lee2015} Lee, J, Kim, G and Yoon, S.
\newblock Measuring large-scale dynamic graph similarity by ricom: RWR with intergraph compression. 
\newblock {\em In 2015 IEEE International Conference on Data Mining, ICDM 2015}, Atlantic City, NJ, USA, November 14-17, 2015, pages 829–834, 2015.


\bibitem {Haussler1999} Haussler, D. 
\newblock Convolution kernels on discrete structures.
\newblock {\em Technical Report}, UCS-CRL-99-10, University of California at Santa Cruz, Santa Cruz, CA, USA, 1999.

\bibitem {Bai2015} Bai, l, Zhang, Z,  Wang, C,  Bai, X and Hancock, E.R.
\newblock A graph kernel based on the Jensen-Shannon representation alignment. 
\newblock {\em In Proceedings of the 24th International Conference on Artificial Intelligence (IJCAI'15)}, Qiang Yang and Michael Wooldridge (Eds.). AAAI Press 3322-3328, 2015.


\bibitem {Aziz2013} Aziz,F, Wilson, R.C. and Hancock, E.R.
\newblock Backtrackless walks on a graph.
\newblock {\em Neural Networks and Learning Systems, IEEE Transactions on}, 24(6):977–989, June, 2013.

\bibitem {Vishwanathan2010} Vishwanathan, S.V.N, Schraudolph, N.N, Kondor, R and Borgwardt, K.M.
\newblock Graph kernels. 
\newblock {\em J. Mach. Learn. Res.}, 11:1201–1242, August, 2010.


\bibitem {Neumann2015} Neumann, M,  Garnett, R,  Bauckhage, C and Kersting, K. \newblock Propagation kernels: efficient graph kernels from propagated
information. 
\newblock {\em Machine Learning}, 102(2):209–245, 2015.

\bibitem {Gartner2003} G{\"a}rtner, T, Flach, P and Wrobel, S. 
\newblock On graph kernels: Hardness results and efficient alternatives.
\newblock In Sch {\"o}lkopf, B and Warmuth, M.K. editors,
\newblock {\em Proceedings of the Annual Conference on Computational Learning Theory}, pages 129–143. Springer, 2003.

\bibitem {Borgwardt2005} Borgwardt, K.M, Ong, C.S,   Sch {\"o}nauer, S, Vishwanathan, S. V. N, Smola, A.J, and Kriegel, H.P.
\newblock Protein function prediction via graph kernels.
\newblock {\em In Proceedings of Intelligent Systems in Molecular Biology (ISMB)}, Detroit, USA, 2005.


\bibitem {Kashima2003} Kashima, H,  Tsuda, K and Inokuchi, A. 
\newblock Marginalized kernels between labeled graphs. 
\newblock {\em In Proceedings of the Twentieth International Conference on Machine Learning}, pages 321–328. AAAI Press, 2003.

\bibitem {Kang2012} Kang, U, Tong, H and Sun, J.
\newblock Fast Random Walk Graph Kernel.
\newblock {\em SIAM International Conference on Data Mining (SDM)}, Anaheim, California, USA, 2012.

\bibitem {Mahe2004} Mah{\' e}, P,  Ueda, N, Akutsu, T, Perret, J.L, and  Vert, J.P. \newblock Extensions of marginalized graph kernels. 
\newblock {\em In Proceedings of the Twenty-first International Conference on Machine Learning, ICML ’04}, pages 70–, New York, NY, USA, 2004.

\bibitem {Sugiyama2015} Sugiyama, M and Borgwardt, K. 
\newblock Halting in random walk kernels.
\newblock {\em In Advances in Neural Information Processing Systems},pages 1630–1638. Curran Associates, Inc., 2015.


\bibitem {Kriegel2005}  Kriegel, H.P and Borgwardt, K.M.
\newblock  Shortest-Path Kernels on Graphs. 
\newblock {\em In Proceedings of the Fifth IEEE International Conference on Data Mining (ICDM '05)},. IEEE Computer Society, Washington, DC, USA, 74-81, 2005.

\bibitem {Martino2012}  Martino, G.D.S,  Navarin, N and  Sperduti, A.
\newblock A Tree-Based Kernel for Graphs.
\newblock {\em Proceedings of the 2012 SIAM International Conference on Data Mining}, pp 12-24, 2012.

\bibitem {Feragen2013} Feragen, A, Kasenburg, N, Petersen, J, Bruijne, D. M and Borgwardt, K.
\newblock Scalable kernels for graphs with continuous attributes.
\newblock {\em Advances in Neural Information Processing Systems 26}, page 216--224, Curran Associates, Inc., 2013.

\bibitem {Yanardag2015B} Yanardag, P and Vishwanathan, S. V. N. 
\newblock A Structural Smoothing Framework For Robust Graph Comparison. \newblock {\em NIPS 2015}, 2134-2142, 2015.

\bibitem {Kondor2016} Kondor, R and Pan, H.
\newblock The Multiscale Laplacian Graph Kernel.
\newblock {\em CoRR}, arXiv:1603.06186 
\newblock \url {http://arxiv.org/pdf/1603.06186v1.pdf}, 2016.

\bibitem {Perozzi2014} Perozzi, B,  Al-Rfou, R and Skiena, S.
\newblock DeepWalk: online learning of social representations. 
\newblock {\em In Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining (KDD '14)}, ACM, New York, NY, USA, 701-710, 2014.

\bibitem {Kandola2003} Kandola, J, Graepel,T and Taylor, J.S.
\newblock  Reducing kernel matrix diagonal dominance using semi-definite
programming. 
\newblock {\em In Proc. Annual Conf. Computational Learning
Theory, volume 2777 of Lecture Notes in Computer Science}, pages 288–302, Washington, DC, 2003.

\bibitem {Milkov2013} Mikolov, T, Sutskever, I, Chen, K, Corrado, G.S, and Dean, J. \newblock Distributed representations of words and phrases and their compositionality. 
\newblock {\em In Advances in neural information processing systems}, pp. 3111–3119, 2013.


\end{thebibliography}
